Illustrating Model Properties

### 2024-07-22 model.qmd
adapt risk plot to new risks

contents = {"II": [], "III": [], "IV": []}
mean_lists = {"II": [], "III": [], "IV": []}
defaults = {
  "density": True,
  "histtype": "stepfilled",
  "alpha": 0.7,
  "bins": 50,
}
t_stage_map = {"early": "early", "late": "adv."}
midext_map = {False: "lateralized", True: "mid. ext."}
colors = [COLORS["green"], COLORS["blue"], COLORS["orange"], COLORS["red"]]

@@

def get_label(scenario: Scenario) -> str:
  t = scenario.t_stages[0]
  m = scenario.midext
  d = eval(scenario.diagnosis)
  return f"{t_stage_map[t]}; {midext_map[m]}; {get_diag_label(d)}"

@@

indices = {}
for lnl, means in mean_lists.items():
  indices[lnl] = np.argsort(means)

counter = {"II": 0, "III": 0, "IV": 0}
with h5py.File(name=paths.model_dir / "full" / "risks.hdf5", mode="r") as h5file:
  for dset in h5file.values():
    scenario = Scenario.from_dict(dict(dset.attrs))
    for_subplot = list(eval(scenario.involvement)["contra"].keys()).pop()
    c = counter[for_subplot]
    counter[for_subplot] += 1
    contents[for_subplot].append(
      Histogram(
        values=dset[:],
        kwargs={
          "label": get_label(scenario),
          "color": colors[indices[for_subplot][c]],
        },
      )
    )

xlims = {
  "II": (0, 15),
  "III": (0, 7),
  "IV": (0, 5),
}
for ax, (lnl, content) in zip(axes, contents.items()):
  draw(ax, content, xlims=xlims[lnl])
  ax.set_title(f"Contralateral LNL {lnl}")
  ax.set_yticks([])
  ax.set_xlabel("risk [%]")
  ax.legend(labelspacing=0.1)

axes[0].set_xticks(np.linspace(xlims["II"][0], xlims["II"][1], 6))

>>>>

contents = {"II": [], "III": [], "IV": []}
mean_lists = {"II": [], "III": [], "IV": []}
defaults = {
  "density": True,
  "histtype": "stepfilled",
  "alpha": 0.7,
  "bins": 50,
}
t_stage_map = {"early": "early", "late": "adv."}
midext_map = {False: "lateral", True: "mid-ext"}
colors = [COLORS["green"], COLORS["blue"], COLORS["orange"], COLORS["red"]]

@@

def get_label(scenario: Scenario) -> str:
  lnl = list(eval(scenario.involvement)["contra"].keys()).pop()
  d = eval(scenario.diagnosis)
  has_upstream_fna = "FNA" in d["contra"]

  if lnl == "IV":
    return get_diag_label(d) + (" & c:III FNA+" if has_upstream_fna else "")

  m = scenario.midext

  if lnl == "III":
    return f"{midext_map[m]}; {get_diag_label(d)}" + (" & c:II FNA+" if has_upstream_fna else "")

  t = scenario.t_stages[0]
  return f"{t_stage_map[t]}; {midext_map[m]}; {get_diag_label(d)}"

@@

indices = {}
for lnl, means in mean_lists.items():
  indices[lnl] = np.argsort(np.argsort(means))

counter = {"II": 0, "III": 0, "IV": 0}
with h5py.File(name=paths.model_dir / "full" / "risks.hdf5", mode="r") as h5file:
  for md5, dset in h5file.items():
    scenario = Scenario.from_dict(dict(dset.attrs))
    for_subplot = list(eval(scenario.involvement)["contra"].keys()).pop()
    c = counter[for_subplot]
    counter[for_subplot] += 1
    contents[for_subplot].append(
      Histogram(
        values=dset[:],
        kwargs={
          "label": get_label(scenario),
          "color": colors[indices[for_subplot][c]],
        },
      )
    )

xlims = {
  "II": (0, 15),
  "III": (0, 9),
  "IV": (0, 7),
}
for ax, (lnl, content) in zip(axes, contents.items()):
  draw(ax, content, xlims=xlims[lnl])
  ax.set_title(f"Contralateral LNL {lnl}")
  ax.set_yticks([])
  ax.set_xlabel("risk [%]")

axes[0].set_xticks(np.linspace(xlims["II"][0], xlims["II"][1], 6))
axes[0].legend(labelspacing=0.1)
axes[1].legend(
  title="advanced T-category",
  title_fontsize="small",
  labelspacing=0.1,
)
axes[2].legend(
  title="advanced T-category\n& midline extension",
  title_fontsize="small",
  labelspacing=0.1,
)
